Computing likelihoods under the SMC for a general class of ARGs.

### 2024-07-11 paper.tex
Minor tweak to caption

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/smc_custom_2rows_area_full_hap.png}
\caption{ARG generated under the SMC, represented as a graph (top) and as a
series of local trees (bottom). To ensure the one-to-one correspondence
between both representations a node is recorded for each local tree whenever
a node is encountered along its ancestry path in the graph representation.
This results in nodes that (locally) have only a single child, and are therefore
(locally) unary. By removing recombinant nodes, we limit the information on the time to each
of these events to the windows (blue shaded array) delimited by by the age of
the child node and the minimum age of the parents of the edges connecting to that child node.
Blue (unary) nodes represent recombinant nodes. The blue arrows show the
familiar left-to-right logic of the SMC whereby
the floating lineage coalesces randomly
with a the remaining portion of the local tree following recombination.
}
\label{fig:smc-unary}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/smc_custom_2rows_area_full_hap.png}
\caption{ARG generated under the SMC, represented as a graph (top) and as a
series of local trees (bottom). To ensure the one-to-one correspondence
between both representations a node is recorded for each local tree whenever
a node is encountered along its ancestry path in the graph representation.
This results in nodes that (locally) have only a single child, and are therefore
(locally) unary. 
Nodes A, B and C are recombinants, i.e, have two parents in the graph
and are unary in the local trees. The blue shaded regions indicate
the range of possible times associated with these recombinants.
The blue arrows show the
standard left-to-right logic of the SMC whereby
the floating lineage coalesces randomly
with a the remaining portion of the local tree following recombination.
% By removing recombinant nodes, we limit the information on the time to each
% of these events to the windows (blue shaded array) delimited by the age of
% the child node and the minimum age of its parents.
}
\label{fig:smc-unary}
\end{figure}
